A numerical study of fixation probabilities for strategies in the Iterated Prisoner's Dilemma

### 2017-04-20 tex/main.tex
Add a table of linear regression coefficients.
This is neat (I think) as it shows numerically that the N=2 case has
very little to do with an actual population dynamic.

>>>>

Tables~\ref{tbl:linear_coeficients_std} and~\ref{tbl:linear_coeficients_noisy}
show the coefficients and \(R^2\) value of the linear model relating the rank in
a particular sized population to the ranks in other populations sizes.
% TODO Discuss these tables: show that none of the models are great (R^2) BUT it
% does show that the coefficient of the N=2 column is always low whereas the
% coefficient of the N=14 column is high even in the N=4 row. So how well you do
% in  a match (N=2) has got very little to do with an evolutionary process.

\begin{table}[!hbtp]
    \begin{subfigure}{.5\textwidth}
        \centering
        \input{"../tbl/linear_coeficients_std.tex"}
        \caption{Linear model coefficients for ranks without noise}
        \label{tbl:linear_coeficients_std}
    \end{subfigure}%
    ~
    \begin{subfigure}{.5\textwidth}
        \centering
        \input{"../tbl/linear_coeficients_noisy.tex"}
        \caption{Linear model coefficients for ranks with noise}
        \label{tbl:linear_coeficients_noisy}
    \end{subfigure}
    \caption{Linear coefficients}
\end{table}
